### 2016-09-28 rebuttal.tex

\usepackage{xr-hyper}
\usepackage{hyperref}
\externaldocument[P-]{paper}

\usepackage{upquote}
\usepackage{textcomp}
\usepackage[T1]{fontenc}

\usepackage{pdfpages}

\hypersetup{
  colorlinks=true,
  filecolor=black, % color of cross-file links. Black because they only work
                   % if the paper sits alongside the rebuttal as "paper.pdf".
  urlcolor=blue % color of external links
}

@@

\question Lines 359 and 379: what is 2D text representation? It seems that ``2D'' shouldn't be here.
\begin{solution}
This sentence was replaced with:
\begin{quote}
A two-dimensional (2D) textual representation of the expression can
be printed with monospace fonts via \verb|pprint|.
\end{quote}
We use here the same terminology as in the Mathematica
online documentation, e.g., the
\href{https://reference.wolfram.com/language/ref/OutputForm.html}{\texttt{OutputForm}}
function:
\begin{quote}
\texttt{OutputForm[expr]}: prints as a two-dimensional representation of expr using only keyboard characters.
\end{quote}
\end{solution}

\question Line 427: every dictionary is a ``dictionary of keys''. This should be a dictionary with coordinate tuples as keys associated with the appropriate values.
\begin{solution}
``Dictionary of Keys'' (DOK) refers specifically to a sparse matrix
representation where entries are stored as \texttt{(row, column)} pairs
mapping to the elements. See for instance \texttt{scipy.sparse.dok\_sparse}. We
have fixed the capitalization of ``Dictionary of Keys'' and added the
abbreviation (DOK), and stated explicitly what is meant by this. We have also
made a similar note about List of Lists (LIL) earlier in the section.
\end{solution}

\question Section 4 would benefit from an introduction, and lines 440-- should become a new subsection 4.1. (named ``Float'' or ``Real numbers support'' or similar).
\begin{solution}
We have added an introduction and a subsection ``Floating-Point Numbers''
(which, for mathematical clarity, we consider to be distinct from ``real
numbers'').
\end{solution}

\question I suggest a better example for lines 459--460: a computation of
$(e^{100} +1) - e^{100}$:

### 2016-09-28 coverletter.tex

\usepackage{graphicx}

@@

\date{September 31, 2016} % stand-in
\begin{document}

@@

We thank you and the referees for your thoughtful comments and suggestions on
our manuscript, ``SymPy: Symbolic Computing in Python''. We have endeavored to
address your comments and concerns point by point below. Below we give your
and the reviewers' comments on white background and our replies on gray
background.

>>>>

\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{geometry}

@@

\date{September 31, 2016} % stand-in

\geometry{headheight = 0.6in}
\fancypagestyle{empty}{\fancyhf{}\fancyhead[L]{\includegraphics[height=1in, keepaspectratio=true]{logo-curves.png}}}

\begin{document}

@@

We thank you and the referees for your thoughtful comments and suggestions on
our manuscript, ``SymPy: Symbolic Computing in Python''. We have endeavored to
address your comments and concerns point by point below. We give your
and the reviewers' comments on white background and our replies on gray
background.
